Sketch of DP - Bayesian Inference

### 2018-07-18 main-sketch.tex
pass on concnlusions and futre work

\begin{theorem}[Privacy] 
  For  $\gamma=\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, both
  $\hexpmech$ and $\hexpmechd$ are $(\epsilon,\delta)$-differentially private.
\end{theorem}

@@

\section{Conclusions and Future Works}
We can obtain some preliminary conclusions:
\begin{enumerate}
  \item We can beat Laplace mechanism when data size is small.
  \item We will beat Laplace mechanism when observed data are more
balanced.
  \item When prior distribution grow larger, we perform better and
better and beat Laplace mechanism finally.
\end{enumerate}

In conclusion, our mechanism has better accuracy in small data size,
larger prior and balanced data. But this is not enough for
application. We will continue our work in following three aspects:
\begin{enumerate}
  \item For now, we just have a intuitive impression on the accuracy
behavior of our mechanism, not a precise formula or bound on it.  When
will we beat the baseline mechanism and when will not? How much
influence will elements in Sec. \ref{sec_experiment} have on the
accuracy? Are there any other important factors we missed? These are
three problems w.r.t. the accuracy we are going to explore next.
  \item The $(\epsilon, \delta)-$dp is a privacy bound of our
exponential mechanism $\hexpmech$ and $\hexpmechd$, but not a tight
bound. The real privacy in experiments can be smaller than it. This
means we can improve our accuracy in a way that increase the privacy
bound but still achieve $(\epsilon, \delta)-$dp.
  \item Our main idea is to have a mechanism based on metric over
distribution but not numeric. The metric we are using is Hellinger
distance here. It is worth to explore other distribution distance
metric, for example, KL-divergence.
\end{enumerate}

>>>>

\begin{theorem}[Privacy] 
\label{thm:privacy}
  For  $\gamma=\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, both
  $\hexpmech$ and $\hexpmechd$ are $(\epsilon,\delta)$-differentially private.
\end{theorem}

@@

\section{Conclusions and Future Works}
From what we have seen in the previous sections 
we can obtain some preliminary conclusions. That is,
the probabiliy measure approach outperforms the $\ell_1$-norm approach in the following cases: 
\begin{enumerate}
  \item When the data size is small
  \item When the observed data is balanced
  \item When priors parameters increase (eventually).
\end{enumerate}

These results although very motivating, are still not enough for real world applications.
Hence, we will continue our work in the follwoing directions:
\begin{enumerate}
  \item For now, we just have a intuitive idea on the accuracy
    behavior of our mechanisms, and not a precise formula or bound on it.
    When do our mechanisms perform better than the baseline mechanism and when they don't?
    How much influence will elements in Section \ref{sec_experiment} have on the
    accuracy? Are there any other important factors we missed? These are
    all questions w.r.t. the accuracy that we are going to explore next, and in a more
    principled and formal way.
\item  Theorem \ref{thm:privacy} provides an upper bound to the  privacy loss for
  $\hexpmech$ and $\hexpmechd$ but  not necessarily a tight one.
  Indeed, experiments have shown that the actual privacy loss in the experiments can be smaller than $\epsilon$.
  This means that we could improve accuracy, by adding less noise --
  that is noise proportional to a higher value of $\epsilon$-- but still achieve $(\epsilon, \delta)$-dp.
\item The choice of the Hellinger distance might seem quite ad-hoc. Hence,
  it is worth exploring other distances over distributions. An interesting class
  of probability metrics is the family of  $f$-divergences \cite{??}.
\end{enumerate}
